Combining information from photometric and spectroscopic data:\\ Don't waste your time in spectrophotometric calibration!

### 2014-04-27 tex/ms.tex
starting on experiments section

>>>>

As a demonstration and test of the methodology for spectrophotometric
calibration described above, we will apply it to an \emph{actual,
  real} optical spectrum of a stellar cluster in M31.  Spectra of star
clusters provide a good test case, as they are less complex than
galaxy spectra (for which it is necessary to model the star formation
history) but are by no means trivial. In this way the key features of the
calibration model and methodology are not obscured, but the influence
of the .

We model the stellar cluster as a single age SSP. The physical
parameters $\theta$ which affect the spectrum of a star
cluster include the age, metallicity, stellar mass, attenuation by dust,
velocity dispersion, redshift, and uncertain
aspects of the stellar population synthesis models, including the
intial mass function.

The model for the spectrum is then 
\begin{eqnarray}
F(\lambda_o, \theta) = G(\sigma_v) \ast m_* S(\lambda_e/(1+z), Z, t,
imf [, {\rm etc}]) e^ {-k_\lambda \tau_V}
\end{eqnarray}
